Mixture Models for Single--Cell Assays with Application to Vaccine Studies

### 2012-09-14 MIMOSA.tex
updated iterations required for convergence
Signed-off-by: Greg Finak <gfinak@fhcrc.org>

\noindent\textbf{MCMC algorithm}\\
We generated realizations from the posterior distribution via MCMC algorithms~\citep{Gelfand:1996wc}. All updates were done via Metropolis-Hastings sampling except for the $z_i$'s and $w$ that were performed via Gibbs samplings.
Details about the algorithms are given in Web Appendix A. We used the method of \cite{Raftery:1992vp} and \cite{Raftery:1996ws} to determine the number of iterations, based on a short pilot run of the sampler. For each dataset presented here, we calculated that no more than about 1,000,000 iterations with 50,000 burn-in iterations was sufficient to estimate standard posterior quantities. To leave some margin, we used 2,000,000 iterations after 50,000 burn-in iterations for each dataset explored here.

>>>>

\noindent\textbf{MCMC algorithm}\\
We generated realizations from the posterior distribution via MCMC algorithms~\citep{Gelfand:1996wc}. All updates were done via Metropolis-Hastings sampling except for the $z_i$'s and $w$ that were performed via Gibbs samplings.
Details about the algorithms are given in Web Appendix A. We used the
method of \cite{Raftery:1992vp} and \cite{Raftery:1996ws} to determine
the number of iterations, based on a short pilot run of the
sampler. For each dataset presented here, we calculated that no more
than about 100,000 iterations with 50,000 burn-in iterations was sufficient to estimate standard posterior quantities. To leave some margin, we used 200,000 iterations after 50,000 burn-in iterations for each dataset explored here.
